Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-25 bbbq_article.tex
Progress https://github.com/richelbilderbeek/bbbq_article/issues/193

HIERO
Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
See \ref{fig:rel_presentation}
\ref{fig:rel_presentation_per_haplotype.png}

fig_rel_presentation_per_haplotype.png

@@

To determine the additional over-presentation of TMH-derived epitopes 
in MHC-II (as compared to MHC-I), we used the same normalized percentages
for the human proteome only and compared the averages between MHC-I and MHC-II.
Figure \ref{fig:fig_rel_presentation_per_haplotype} shows the normalized
TMH-derived epitope presentation per haplotype.

See figure \ref{fig:fig_rel_presentation}.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_rel_presentation_per_haplotype.png}
  \caption{
    Normalized proportion of MHC-I and MHC-II epitopes overlapping with TMHs
    for human proteomes.
  }
  \label{fig:fig_rel_presentation_per_haplotype}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_rel_presentation.png}
  \caption{
    Normalized proportion of MHC-I and MHC-II epitopes overlapping with TMHs
    for human proteomes.
  }
  \label{fig:fig_rel_presentation}
\end{figure}

>>>>

Additionally, we investigated if MHC-I and MHC-II are equally prone
to present TMH-derived epitopes. 
\richel{Add exact method}
See \ref{fig:rel_presentation} and \ref{fig:rel_presentation_per_haplotype}.

@@

To determine the additional over-presentation of TMH-derived epitopes 
in MHC-II (as compared to MHC-I), we used the same normalized percentages
and compared the averages between MHC-I and MHC-II.
Figure \ref{fig:rel_presentation_per_haplotype} shows the normalized
TMH-derived epitope presentation per haplotype.
To compare the TMH-derived over-presentation per MHC class, 
we plot the mean and standard error of the normalized values,
grouped per haplotype in figure \ref{fig:rel_presentation}.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_rel_presentation_per_haplotype.png}
  \caption{
    Normalized proportion of MHC-I and MHC-II epitopes overlapping with TMHs,
    for the different haplotypes and proteomes
  }
  \label{fig:rel_presentation_per_haplotype}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_smart_results/fig_rel_presentation.png}
  \caption{
    Normalized proportion of MHC-I and MHC-II epitopes overlapping with TMHs,
    for the different MHC classes and proteomes. Error bars denote the
    standard error.
  }
  \label{fig:rel_presentation}
\end{figure}
